Supplementary Figures: Eco-evolutionary dynamics and collective migration: implications for salmon metapopulation robustness

### 2017-09-13 Manuscript/FinalDraft_rev/supp.tex
some more edits to rev

@@

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{fig_mthetarelation.pdf}
\caption{
In some cases, habitat heterogeneity may be assumed to determine the rate of straying, if for example:
1) sites may be distributed over greater spatial distances, where habitat differences are assumed to be greater between more distant sites, or 2) individuals have behaviors promoting dispersal between habitats that are more similar. To examine such cases, we use the relationship $m= 0.5(1 + \Delta\theta)^{-1}$ where maximum straying is assumed to occur at $m=0.5$ (perfect mixing).
} \label{fig:mthetarelation}
\end{figure}

>>>>

\begin{figure}
  \captionsetup{justification=raggedright,
singlelinecheck=false
}
\centering
\includegraphics[width=0.35\textwidth]{fig_mthetarelation.pdf}
\caption{
In some cases, habitat heterogeneity may be assumed to determine the rate of straying, if for example:
1) sites are distributed over greater spatial distances, where habitat differences are assumed to be greater between more distant sites, or 2) individuals have behaviors promoting dispersal between habitats that are more similar. To examine such cases, we use the relationship $m= 0.5(1 + \Delta\theta)^{-1}$ where maximum straying is assumed to occur at $m=0.5$ (perfect mixing).
} \label{fig:mthetarelation}
\end{figure}

@@
